### 2015-05-01 analysis/e5_analysis.Rmd
e6 plus models
revised contexts

```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment))

@@

>>>>

```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            p = (judgment - 1)/4)

@@

barplot

```{r}
qplot(stars, judgment, facets = degree ~ scale, 
      geom="bar", stat = "identity",
      binwidth = 1, data=ms)
```

difference scores

```{r}
ms.delta <- ms %>% 
  select(-cil, -cih) %>%
  spread(degree, judgment) %>%
  mutate(delta = ifelse(scale != "liked_loved", hi - low, low - hi))

pdf("plots/e5_delta.pdf", width = 8, height = 3)
qplot(stars, delta, facets = . ~ scale, geom = "line",
      data = ms.delta) + 
  geom_hline(yintercept = 0, lty=2)
dev.off()
```
